---
title: "how-to-use-MapR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{how-to-use-MapR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette provides an overview on how to use MapR. MapR is an App to display temporal and temperature graphical files for Isomemo.

## Introduction

To work with MapR, a zip file is needed, which can be uploaded after starting the app. It is also possible to select an online zip file that contains example data. The zip file must contain both the images to be displayed (stored in a folder called `data`) and a `json` file that specifies which images are displayed depending on the users selection.

The `json` file can be an image list (`image_list.json`) that contains group-, variable- and measure names and the image belonging to each combination of these three. Also for each image, the path where the image can be found in the `data` folder, must be included.

Alternatively, the `json` file can be a questionnaire (`questionnaire.json`). The file must contain questions that are displayed to the user. Furthermore the file must contain the images to be displayed with the information which answer is needed to display a specific image. Also the path where the image can be found in the `data` folder, must be included again.

Both the `image_list.json` file or the `questionnaire.json` must have the same structure as provided in the [example zip files](https://github.com/Pandora-IsoMemo/MapR/tree/beta/inst/app/exampleZip).

Some fields need more attention because only specific values are supported by the app:

Within both json files the field `file_type` must be "png" or "nc". 

Within `questionnaire.json`

- the field `Type` belonging to `Questions` can be either "multiple choice" or "numeric".
  - If "multiple choice" is selected, the field `Answers` must contain a list of possible answers (see example files).
  - If "numeric" is selected, the field `Answers` should be empty. Additionally, one can specify a `Fill_Value` which is prefilled into the input field. If `Fill_Value` is an empty string (`""`), the input field is empty.

-  the field `Type` belonging to `Plots` can be any mathematical operator (e.g. `>`, `<=`, `==`, `!=`, `>=`, `<`).

## Usage

To start the app one can use the online version or run the following command locally:

```{r, eval=FALSE, setup}
library(MapR)
startApplication()
```

After starting the app a zip file must be uploaded by clicking on the `Import ZIP file` button. Depending on the concent of the zip file (`image_list.json` or `questionnaire.json`), the app will display different inputs that can be filled out by the user. Finally, by clicking on the button `Display plot`, the image can be displayed.
